Data Management \\ and LSST Special Programs

### 2022-02-20 DMTN-065.tex
done w S 2.4

Generally, Rubin Observatory might incorporate Special Programs data into the data products for the WFD Main Survey whenever this is (1) possible and (2) scientifically beneficial.
{\bf Decisions about when and whether to do this are left to the discretion of the Rubin Operations Data Production and System Performance teams.}

\subsubsection{Prompt Processing}

@@

\subsubsection{Data Release Processing}

@@

\subsection{Anticipated Unique and Separate Special Programs Data Products}\label{ssec:proc_spdp}

@@

The anticipated divisions between what will be Rubin- versus User-Generated for the variety of anticipated ``unique and separate" Special Programs data products, which are designed to meet the specific science goals of the Special Programs, are {\it preliminarily} described.
{\bf Decisions about when and whether to do this are left to the discretion of the Rubin Operations Data Production and System Performance teams.}

@@

{\bf Rubin-generated data products} might include:\\
 - nightly-coadded images (24 h)\\
 - nightly-coadded difference images (24 h)\\
 - deeply-coadded images (all images to date; yearly)\\
 - templates for the nightly-coadded difference images (yearly)\\
 - Source- and Object-like catalogs for the night and deep coadds (yearly)\\
 - DIASource- and DIAObject-like catalogs for the nightly-coadds (24 h)\\

{\bf User-Generated data products} might include, for example, DDF images coadded on other timescales, or using algorithms outside of the LSST Science Pipelines.

@@

@@

\subsubsection{Deeper $g$-band for 10 Local Volume Galaxies}

@@

For example, the additional sky areas covered with a cadence and depth that is different from the WFD Main Survey, such as the proposed Special Programs for the Roman bulge field; deeper $g$-band imaging of 10 local volume galaxies; the SMC; the Carina nebula; the northern stripe; and the Virgo Cluster.

>>>>

Generally, Rubin Observatory might incorporate Special Programs data into the data products for the WFD Main Survey whenever this is (1) possible and (2) scientifically beneficial.
{\bf Decisions about when and whether to include Special Programs data in the WFD Main Survey's data products are left to the discretion of the Rubin Operations Data Production and System Performance teams.}

\subsubsection{Prompt}

@@

\subsubsection{Data Release}

@@

\subsection{Anticipated Rubin- and User-Generated Special Programs Data Products}\label{ssec:proc_spdp}

@@

The anticipated divisions between what will be Rubin- versus User-Generated for the variety of anticipated ``unique and separate" Special Programs data products, which are designed to meet the specific science goals of the Special Programs, are {\it preliminarily} described.
{\bf Decisions about when and whether Rubin Observatory will generate Special Programs data products are left to the discretion of the Rubin Operations Data Production and System Performance teams.}

@@

Rubin-generated data products might include:\\
 - nightly-coadded images (24 h)\\
 - nightly-coadded difference images (24 h)\\
 - deeply-coadded images (all images to date; yearly)\\
 - templates for the nightly-coadded difference images (yearly)\\
 - Source- and Object-like catalogs for the night and deep coadds (yearly)\\
 - DIASource- and DIAObject-like catalogs for the nightly-coadds (24 h)\\

User-Generated data products might include, for example, DDF images coadded on other timescales, or using algorithms outside of the LSST Science Pipelines.

@@

If the Rubin Operations team decides that the LSST Science Pipelines can be reconfigured and used for short exposures, then the Rubin-generated data products would likely be similar to the Data Release data products (Section 4, \citeds{lse-163}).
For example, a separate repository of processed visit images and coadded images, and separate (but joinable) {\tt Source}, {\tt Forced Source}, and {\tt Object} catalogs.

@@

As the science goals of any target-of-opportunity program are the immediate processing and discovery of new transient phenomena, it is very likely that all ToO programs would be designed to use standard or alternative standard visits and Prompt processing data products such as Alerts.
Prompt processing would proceed automatically for all ToO for which an LSST template image exists.

Options for Rubin Observatory to assist with or expedite the processing of ToO programs, especially during the first year of Operations when the template coverage will be low, are discussed in more detail in \citeds{rtn-008}.

Other science-driven data products from ToO programs, such as custom deep stacks and difference images to find $<$5$\sigma$ transients in the fields on intermediate timescales in cases where the optical counterpart was not detected, would require User-Generated processing.

@@

Potential micro-surveys include additional sky areas, in some cases covered to a depth that is different from the WFD Main Survey, such as the proposed micro-surveys for the Roman bulge field; deeper $g$-band imaging of 10 local volume galaxies; the SMC; the Carina nebula; the northern stripe; and the Virgo Cluster.

In all of these cases, if the Rubin Operations team decides that the LSST Science Pipelines can be reconfigured and used for the visits associated with these micro-surveys -- which is likely if they're using standard or alternative standard visits --  then the Rubin-generated data products would be similar to the Data Release data products (Section 4, \citeds{lse-163}).
For example, separate repositories of processed visit images and coadded images, and separate (but joinable) {\tt Source}, {\tt Forced Source}, and {\tt Object} catalogs would be created for all of these micro-surveys.

In cases where data for the micro-survey is obtained throughout the year, then the separate data products would also be produced on a yearly basis.
In cases where the data might be all obtained within a week (e.g., Carina nebular survey), such data products would likely be generated on a shorter (intermediate) timescales.

Micro-surveys with time-domain science goals that aren't met by the Prompt pipelines -- for example if they require difference imaging with coadded images on an intermediate timescale (e.g., a weekly stack) --  might require User-Generated processing.
